Exploring probability distributions for bivariate temporal granularities

### 2019-11-27 main.Rmd
linear and granule fixed

  (C1) if $i < j$ and $G(i)$ and $G(j)$ are non-empty, then each element of $G(i)$ is less
than all elements of $G(j)$, and  
  (C2) if $i < k < j$ and $G(i)$ and $G(j)$ are non-empty, then $G(k)$ is non-empty.  
\end{timedom}

**Dicussion:** Each non-empty subset $G(i)$ is called a **granule**, where $i$ is one of the indexes and $G$ is a linear granularity. The first condition implies that the granules in a linear granularity are non-overlapping and their index order is same as time order.
\autoref{fig:linear-time} shows the implication of this condition. If we consider the chronon [@aigner2011visualization] as hourly, the time domain with T hours will have $\lfloor T/24\rfloor$ days, $\lfloor T/(24*7)\rfloor$ weeks and so on.

@@

**Dicussion:** According to this definition, $G \trianglelefteq H,$ if each granule H (j) is the union of some
granules of G. For example, $Days \trianglelefteq Months$. However, this  relationship is not fully described until we associate it with periodicity. For example, $Days \trianglelefteq Months,$, since each month is a grouping of a number of days, however it is also a periodical grouping. If leap year is ignored, the periodicity of the grouping is 1 year, since each month would be defined as the grouping of the same number of days (31, 28, or 30, depending on the month) every year. Considering leap years and all their exceptions, the period becomes 400 years.

>>>>

  (1) if $i < j$ and $G(i)$ and $G(j)$ are non-empty, then each element of $G(i)$ is less
than all elements of $G(j)$, and  
  (2) if $i < k < j$ and $G(i)$ and $G(j)$ are non-empty, then $G(k)$ is non-empty.  
\end{timedom}

\begin{timedom}\label{def:granule}
Each non-empty subset $G(i)$ is called a **granule**, where $i$ is one of the indexes and $G$ is a linear granularity.
\end{granule}

**Dicussion:** The first condition in \ref{def:linear} implies that the granules in a linear granularity are non-overlapping and their index order is same as time order.
\autoref{fig:linear-time} shows the implication of this condition. It shows the linear granularities hours, days, weeks, months and years, each of which are unidirectional in nature and arranged from past to future. If we consider the chronon [@aigner2011visualization] as hourly, the time domain with T hours will have $\lfloor T/24\rfloor$ days, $\lfloor T/(24*7)\rfloor$ weeks and so on. Each granule of the linear granularities shown are represented through a box.

@@

**Dicussion:** According to this definition, $G \trianglelefteq H,$ if each granule H(j) is the union of some granules of G.

For example, $Days \trianglelefteq Months$. However, this  relationship is not fully described until we associate it with periodicity. For example, $Days \trianglelefteq Months,$, since each month is a grouping of a number of days, however it is also a periodical grouping. If leap year is ignored, the periodicity of the grouping is 1 year, since each month would be defined as the grouping of the same number of days (31, 28, or 30, depending on the month) every year. Considering leap years and all their exceptions, the period becomes 400 years.
